While this project is exists purely as a piece
of research rather than a practical tool, it's 
moral and ethical considerations must be taken into
account.

\section{Personal Data}
No personal data was used at all over the course
of this project. All protein sequences were sourced
from \url{https://www.rcsb.org/}, the sources
of the sampled proteins were not identified
or used over the course of this project.

\section{Moral Considerations}
While this project was ultimately unsuccessful,
the moral implications of succesfully being
able to determine a proteins tertiary structure
from its primary sequence alone is far reaching.
Proteins are responsible for all biological
functions within the body, including
the regulation and inhibition of various
hormones, chemicals and cycles within the body.
In addition to that, proteins are also 
responsible for the creation and destruction
of any and all cells in the body, their
critical role in natural biology cannot be 
understated. Should the technology that allows
us to infer a proteins precide tertiary structure
from its primary sequence alone become available,
this would unlock a completely new age of medicine
and potentially body modification. The field
of \emph{de novo} protein design has the potential
to revolutionise personal medicine and healthcare
by designing proteins specific to the individual,
treatements vary from curing Hungtington's diesease
down to modifying our very DNA. Furthermore 
it would be possible to design custom vaccines
for novel viruses within weeks and months rather
than years, the ability to verify the functions
of a protein by quickly iterating on structure
would allow pharmaceutical companies to cheaply
create and distribute effective treatements
that are verifiable safe for patients; side
effects could even be mitigated on a patient
by patient basis by making slight alterations
to the original protein.

That said, this does not prevent the technology
being used for malicious intents. It would also
be possible to engineer weapons of biological 
warfare that could prove to be the ultimate
detriment to humanity. As is common practice,
proteins could be delivered to subjects by encasing
them within viruses. This would permit the mass
dissemination of a potentially harmful biological
weapon.

It is important that such a technology should be regulated
and closely monitored by law enforcement, it must
also be used with extreme caution has it has
the potential not only to affect the individual
but also their descendants.

\section{Copyright}
Code from the orignal authors
\cite{Yang2018} was used as a reference
implementation for the mean field regime,
although the original work was implemented in Tensorflow
and was released to the public as an open source project.
The code present within this project will also be
made open source and publicly available for further 
research under the MIT licence.